Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-10-26 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Closing #43
Closes #43
Issue #37
Correcting; *”Another issue is that some details are described twice,
for instance, the advantages of the use of web workers.”* Closes #37

  Apart from
  these constants, the algorithm can be run in many different ways:
  stopping when a solution is found or, as we have done in this paper,
  using Web Workers, which run in the background even if the webpage or
  browser tab having the experiment is not currently on focus.
\end{enumerate}

@@

At any rate, this also shows that a convenient way of increasing the
computing power would be increasing this minimum amount per user. This
issue led us to create the next version of the framework, which is
presented next. 
\subsection{{\sf NodIO-W$^2$}, a Web Worker-based architecture}

In order to improve the number of cycles per user, we improved the
basic architecture in several different aspects. By using Web Workers 
the algorithm kept running on the background even if the {\sf NodIO}
tab was not in focus. It also allowed several clients to run per
browser, as opposed to a single one as we did previously. Another
improvement involved restarting the client once the solution was
found, so that as long as the user was visiting the page it was
running an evolutionary algorithm. Finally, a small algorithmic
improvement was included: instead of having a fixed population,
population size was randomly distributed between 128 and 256 and
different for each client.

>>>>

  Apart from
  these constants, the algorithm can be run in many different ways:
  stopping when a solution is found or, as we have done in this paper,
  using Web Workers. 
  % Repeated
  %which run in the background even if the webpage or
  %browser tab having the experiment is not currently on focus.
\end{enumerate}

@@

At any rate, this also shows that a convenient way of increasing the
computing power would be increasing this minimum amount per user. This
issue led us to create the next version of the framework, which is
presented next.

\section{{\sf NodIO-W$^2$}, a Web Worker-based architecture}

In order to improve the number of cycles per user, we improved the
basic architecture in several different aspects.  One improvement 
involved restarting the client once the solution was
found, so that as long as the user was visiting the page it was
running an evolutionary algorithm. Another was a small algorithmic
improvement: instead of having a fixed population,
population size was randomly distributed between 128 and 256 and
different for each client.  The other improvment was the 
use the Web Worker API as described next.
